%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

    \usepackage{latexsym}
    \usepackage[empty]{fullpage}
    \usepackage{titlesec}
    \usepackage{marvosym}
    \usepackage[usenames,dvipsnames]{color}
    \usepackage{verbatim}
    \usepackage{enumitem}
    \usepackage[pdftex]{hyperref}
    \usepackage{fancyhdr}
    \usepackage{textcomp}
    \usepackage{xcolor}
    \usepackage{lipsum}
    \usepackage{setspace}
    \usepackage{fontawesome}
    \usepackage{ifsym}
    \usepackage{graphicx}
    \usepackage{fontawesome}

    \pagestyle{fancy}
    \fancyhf{} % clear all header and footer fields
    \fancyfoot{}
    \renewcommand{\headrulewidth}{0pt}
    \renewcommand{\footrulewidth}{0pt}
    
    % Adjust margins
    \addtolength{\oddsidemargin}{-0.375in}
    \addtolength{\evensidemargin}{-0.375in}
    \addtolength{\textwidth}{1in}
    \addtolength{\topmargin}{-.5in}
    \addtolength{\textheight}{1.0in}
    
    \urlstyle{same}
    
    \raggedbottom
    \raggedright
    \setlength{\tabcolsep}{0in}
    
    % Sections formatting
    \titleformat{\section}{
      \vspace{-4pt}\scshape\raggedright\large
    }{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

    %-------------------------
    % Custom commands
    \newcommand{\resumeItem}[2]{
      \item\small{
        \textbf{#1}{: #2 \vspace{-2pt}}
      }
    }
    
    \newcommand{\resumeSubheading}[5]{
      \vspace{-1pt}\item
        \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
          \textbf{#1} & #2 \\
          \textit{\small#3} & \textit{\small #4} \\
        \end{tabular*}\vspace{#5 pt}
    }
    
    \newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
    \newcommand{\methodsTools}[1]{\textbf{\faCog: } #1}
    \renewcommand{\labelitemii}{$\circ$}
    
    \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
    \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
    \newcommand{\resumeItemListStart}{\begin{itemize}}
    \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
    
    %-------------------------------------------
    %%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    \begin{document}
    
    %----------HEADING-----------------
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\href{https://www.linkedin.com/in/fang-han-368b1a124/}{\Large Fang Han}} & \\ 
      \faLinkedin \  \href{https://www.linkedin.com/in/fang-han-368b1a124/}{https://www.linkedin.com/in/fang-han-368b1a124/} & \faMobilePhone \  +1-734-680-3913 \\
      \faGithub \ \href{https://github.com/HanFa}{https://github.com/HanFa} & \Letter  \  \href{mailto:hanfa@umich.edu}{hanfa@umich.edu} \\
      \faGlobe \ \href{http://hanfa.me}{http://hanfa.me} &
    \end{tabular*}
    \vspace{0.5em}
    
    %-----------SELFINTRO-----------------
    Passonate software engineer with 3-year software-related research experience and professionalism in modern web development technologies and machine learning algorithms. Serious about code quality and able to learn new languages quickly.

   %-----------EDUCATION-----------------
   \section{\faBook Education}
   \resumeSubHeadingListStart
     \resumeSubheading
       {\href{http://www.umich.edu}{University of Michigan}}{Ann Arbor, MI}
       {Computer Science B.S.E 3.86/4.00}{Sept. 2016 -- Dec. 2018}{-5}
       \begin{itemize}
         \item All semesters University Honors \& Dean's List
         \item Game Design Project: 
           \begin{itemize}
             \item Recreate Zelda NES version using Unity in C\# together with a customized level individually
             \item Develop a rhythm shooter game: \href{http://www.hanfa.me/projects/index.html#opera-a-rhythm-shooter-game}{\textit{Ultimate Opera Fight}}
           \end{itemize}
         
         
         \item Computer Architecture Capstone Design Project: Design and Implement a 3-way-superscalar R10k pipeline microprocessor using System Verilog. Validate and synthesize the microprocessor architecture
       \end{itemize}
     \resumeSubheading
       {\href{http://umji.sjtu.edu.cn/global/}{UM-SJTU Joint Institute} at Shanghai Jiao Tong University}{Shanghai, China}
       {Electrical and Computer Engineering B.S.E 3.60/4.00}{Sept. 2014 -- Aug. 2018}{-5}
       \begin{itemize}
         \item Outstanding Undergraduate Scholarship \& Dean's List
         \item Software Capstone Design: \href{http://www.hanfa.me/projects/index.html#justgo-integrated-virtual-vehicle-simulation-platform-on-android}{\textit{Vehicle Simulation Platform On Android}} provides the in-vehicle software developers with handy utilities such as dashboard display panels, mock location providers and other operational interfaces
       \end{itemize}
   \resumeSubHeadingListEnd



    %-----------EXPERIENCE-----------------
    \section{\faShoppingBag Research Experience}
    \resumeSubHeadingListStart
    \resumeSubheading
    {Attack Lidar using EMI}{Ann Arbor, MI}
    {SPQR Lab Assistant}{Jan. 2019 - Present}{-5}
    \begin{itemize}
      \item Visualize point clouds in threejs to analyze the effect of electromagnetic interference on Lidar
      \item Propose adversarial machine learning attack methods against Apollo CNN segmentation model
      \item Expose the vulnerability of Apollo CNN model under certain electromagnetic interference, as validated in the software level
    \end{itemize}


    \resumeSubheading
    {Edge Computing Research}{Ann Arbor, MI}
    {System Lab Assistant}{Sept. 2018 - Present}{-5}
    \begin{itemize}
      \item Implement a remote computation architecture for augmented windshield display and facial recognition
      \item Apply the idea of edge computing to stateful applications and evaluate their network performance in terms of latency. Reduce the overhead in cross-nodes data migration using previsioning
    \end{itemize}

    \resumeSubheading
    {Stack-structured L-Tage Branch Predictor}{Ann Arbor, MI}
    {Computer Architecture Research Assistant}{Jun. 2017 - Feb. 2018}{-5}
    \begin{itemize}
      \item Write gem5 C++ source code of a stack-structured branch predictor inherited from L-Tage
      \item Validate different implementations and evaluate the performance in terms of prediction correct rates and instructions per second. Obtain a 3\% performance boost when the new structure is enabled in certain program counters
      \item Tackle technical and programming problems for research lab-mates
    \end{itemize}
    \resumeSubHeadingListEnd

 

    %-----------PROJECTS-----------------
    \section{\faCogs Projects}
      \resumeSubHeadingListStart
        \resumeSubheading{Distributed Computing \& Data Mining}{Shanghai, China}{\href{https://labrosa.ee.columbia.edu/millionsong/}{Million Song Dataset} Analysis}{Jun. 2018 -- Sept. 2018}{-5}
        \begin{itemize}
          \item Exploit open-source distributed computing (\href{https://hadoop.apache.org/}{Apache\textsuperscript{TM} Hadoop}) to analyse the entire 280GB dataset
          \item Extract the data in \texttt{.btf} by a customized storage plugin for \href{https://drill.apache.org/}{Drill}
          \item Apply data analysis on the artist locations and music style. Document the findings in \LaTeX
        \end{itemize}
        \methodsTools{R Studio, Hadoop Ecosystem, Data Visualization, \LaTeX}

        \resumeSubheading{Web Systems}{Ann Arbor, MI}{Insta485 Website Development}{Jan. 2018 -- Apr. 2018}{0}
        Recreate the dynamic Instagram website passing all test cases, including:
        \begin{itemize}
          \item Sqlite3 as user database. Flask for the server-side framework which maintains user sessions and handles different requests such as manage accounts and post photos
          \item React for the client side framework to manage states for each web component. Other \texttt{npm} packages \texttt{infinite-scroll} to provider users with more seamless experience
          \item A search engine for article Wiki, ranked on \href{https://en.wikipedia.org/wiki/Tf%E2%80%93idf}{tf-idf}. The index was calculated using parallelized mapreduce algorithm, supported by Hadoop streaming
        \end{itemize}
        \methodsTools{JetBrain Webstorm, Python3, Flask, React, Hadoop MR Streaming, \texttt{npm}}

        \resumeSubheading{Operating Systems}{Ann Arbor, MI}{Thread Library, Pager, File Systems}{Jan. 2018 -- Apr. 2018}{0}
        Implement operating system kernel and pass all test cases, including:
        \begin{itemize}
          \item Multithreading library above the provided hardware interface
          \item OS pager for memory management
          \item Multiple-user, tree-structured and remote-accessible file system          
        \end{itemize}
        \methodsTools{GNU Thread Library, Sockets, C++}

        \resumeSubheading{Embedded Systems Design}{Ann Arbor, MI}{Package Sorting Robot}{Sept. 2017 -- Dec. 2017}{0}
        Build a \href{http://www.hanfa.me/projects/index.html#package-sorting-robot}{package sorting robot} within a 4-member team, featured in:
        \begin{itemize}
          \item High efficiency and accuracy of packages classification compared with traditional human sorting process
          \item Automatic processing pipeline including delivering (conveyor belt), sorting (camera color detection and object classification), packing (bridge crane and controller) and monitoring (LCD display)
        \end{itemize}
        \methodsTools{SmartFusion FPGA, Fault Tolerant Algorithm Design, UART Protocol Programming}

      \resumeSubHeadingListEnd
    
    %
    %--------Courses------------
    \section{\faBookmark Courses}
    \begin{tabular}{p{7cm}p{7cm}l}
      Database Management System & Computer Networks & Computer Game Design \\
      Methods and Tools for Big Data & Intro to Cryptography & Intro to Operating Systems \\
      Web Systems & Intro to Machine Learning & Embedded Systems \\
      Data Structures \& Algorithms & Computer Architecture \& VLSI Design & Digital Signal Processing
    \end{tabular}

    %
    %--------PROGRAMMING SKILLS------------
    \section{\faTerminal Skills}
     \resumeSubHeadingListStart
       \item \textbf{Generals}{: Independent Research, Software Programming, Teamwork, Techical Communication}
       \item \textbf{Languages}{: 
        \begin{itemize}
          \item $\geq 10000$ lines: Python, Java, C/C++, Javascript, C\#, HTML, CSS, Bash
          \item $\geq 1000$ lines: Ruby, R, SQL
          \item Familiar with: Mathematica, Matlab
        \end{itemize}
       }
       \item \textbf{Technologies \& Softwares:}{Unix, Scikit-learn, Pytorch, TensorFlow, React, Flask, Rails, Android Studio, Unity, FPGA Programming,  \LaTeX, Git, OpenCV,  Hadoop ecosystem (Mapreduce, Drill, Spark, Avro)}
       
     \resumeSubHeadingListEnd
    
    %-------------------------------------------
    \end{document}
    